DisjunctiveProgramming.jl: Generalized Disjunctive Programming Models and Algorithms for JuMP

### 2022-10-13 paper/paper.tex
update version in paper

\subsection{Example}
To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.3.2), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}. In this problem a chemical plant with two candidate reactor technologies ($R_1$ and $R_2$) must be designed. If the second reactor technology is chosen, a separation system must also be installed, for which two separation technologies ($S_1$ and $S_2$) are available. The GDP model seeks to maximize the product flow ($F_7$), while discounting for reactor ($C_R$) and separator ($C_S$) installation costs as given in \eqref{eq:example_obj}, subject to the nested disjunction in \eqref{eq:example_gdp} and the global mass balances in \eqref{eq:example_global}
- \eqref{eq:example_global1}. The system variables are the flows on each stream $i$ ($F_i$) and the installation costs, with their respective bounds given in \eqref{eq:example_var1} - \eqref{eq:example_var3}. The fixed cost and process yield parameters are given by $\gamma$ and $\beta$, respectively.

>>>>

\subsection{Example}
To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.3.3), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}. In this problem a chemical plant with two candidate reactor technologies ($R_1$ and $R_2$) must be designed. If the second reactor technology is chosen, a separation system must also be installed, for which two separation technologies ($S_1$ and $S_2$) are available. The GDP model seeks to maximize the product flow ($F_7$), while discounting for reactor ($C_R$) and separator ($C_S$) installation costs as given in \eqref{eq:example_obj}, subject to the nested disjunction in \eqref{eq:example_gdp} and the global mass balances in \eqref{eq:example_global}
- \eqref{eq:example_global1}. The system variables are the flows on each stream $i$ ($F_i$) and the installation costs, with their respective bounds given in \eqref{eq:example_var1} - \eqref{eq:example_var3}. The fixed cost and process yield parameters are given by $\gamma$ and $\beta$, respectively.
